Mechanisms of AIAN Inequality in Child Welfare Across U.S. States.

### 2020-12-16 cfp_final_report.Rmd
fix icwa with boarding

# afcars_caseload<-read_csv("./data/state_first_fc.csv")%>%
#   filter(.imp==1) %>% 
#   rename(year = fy) %>%
#   filter(state!=72) %>%
#   rename(var = first_entry) %>%
#   rename(st_fips = state) %>% 
#   filter(year == 2018) %>% 
#   mutate(race_ethn = ifelse(race_ethn=="AI/AN",
#                             "AIAN",
#                             "other")) %>% 
#   group_by(st_fips, race_ethn) %>% 
#   summarise(fc = sum(var)) %>% 
#   ungroup() %>% 
#   left_join(pop_seer_nat %>% 
#               filter(age<=21) %>% 
#               select(state, st_fips, age, race_ethn, pop) %>% 
#               group_by(state, st_fips, race_ethn) %>% 
#               summarize(pop = sum(pop)) %>% 
#               ungroup()) %>% 
#   filter(state%in%icwa_fc$state) %>% 
#   ungroup()

### add adoption data

@@

### state comparisons
icwa_delta<-icwa_fc %>% 
  select(-St) %>% 
  mutate(race_ethn = ifelse(race_ethn=="White",
                            "other",
                            race_ethn)) %>% 
  bind_rows(afcars_caseload %>% 
              select(state, period, race_ethn, fc, adopted)) %>% 
  filter(state%in%icwa_fc$state)

>>>>

@@

### state comparisons
icwa_delta<-icwa_fc %>% 
  mutate(race_ethn = ifelse(race_ethn=="White",
                            "other",
                            race_ethn)) %>% 
  bind_rows(afcars_caseload %>% 
              select(state, period, race_ethn, fc, adopted)) %>% 
  filter(state%in%icwa_fc$state)
